### 2019-11-21 thesis/txt/0-introduction.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
Such regular expressions are developed by looking at a few exemplary build logs and updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.

@@

The goal of this thesis is to investigate different chunk retrieval techniques (CR techniques) for build logs and describe under which circumstances each techniques is recommended over another.
We aim to define a model to characterize different CR techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a CR technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when configured with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of examples used in the configuration has no visible influence and fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower recall.
  It is the only technique where retrieval quality does not decrease with an increasing number of structural categories in the configuring examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structurally predictable way and high confidence in the exactness of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, the low precision requires a human to interpret the output of the chunk retrieval.

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the contained and retrievable information in CI build logs.
  \item A model to characterize chunk retrieval techniques from CI build logs.
  %\item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several chunk retrieval techniques namely:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS)
        \end{itemize}
  %\item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log.
        \end{itemize}
  \item A study comparing the effectiveness of the three implemented techniques.
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique. % TODO for a given use case or so?
\end{itemize}

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} presents existing work on information extraction and retrieval techniques and program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques: PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.
\end{document}

>>>>

There are different techniques to retrieve information from CI build logs. Beller et al.\ use regular expressions to analyze the reasons of build failures from Travis CI logs~\cite{beller2017oops}.
Such regular expressions are developed by looking at a few exemplary build logs. Updating them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al.\ wrote a custom parser for build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et al.\ reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and a successful build~\cite{amar2019mining}.

@@

The goal of this thesis is to investigate different chunk retrieval techniques for build logs and describe under which circumstances each techniques is recommended over another.
We aim to characterize different chunk retrieval techniques, as well as the information retrievable from CI build logs.
For \textbf{RQ1}, we analyze which criteria influence the suitability of a chunk retrieval technique for CI build logs.
We implement and evaluate three chunk retrieval techniques:
\begin{itemize}
  \item program synthesis by example using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as CTS) and
  \item keyword search (referred to as KWS)
\end{itemize}
\textbf{RQ2} asks under which conditions PBE, CTS and KWS are suited to retrieve information from continuous integration build logs.
\textbf{RQ2} is refined into sub-questions along with the criteria resulting from \textbf{RQ1} and compares their instantiations for the three techniques:
how many training examples a technique needs to perform best (\textbf{RQ2.1}), how structurally diverse the examples can be (\textbf{RQ2.2}) and the accuracy of the retrieved output (\textbf{RQ2.3}).
% \begin{simplebox}{Research Questions}
% \begin{itemize}
%   \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
%   \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?
%   \item[\textbf{RQ2.1:}] How many examples do PBE, CTS, and KWS need to perform best?
%   \item[\textbf{RQ2.2:}] How structurally similar do the examples for PBE, CTS and KWS need to be for the techniques to be applicable?
%   \item[\textbf{RQ2.3:}] How accurate are the retrievals of PBE, CTS, and KWS?
% \end{itemize}
% \end{simplebox}
To evaluate PBE, CTS and KWS we create a data set, namely \emph{LogChunks}, which encompasses about 800 log files from 80 repositories.
Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural representation within the log.

Our study of the three techniques on \emph{LogChunks} shows that
\begin{itemize}
  \item PBE yields very accurate results when trained with 1 to 3 examples from a single structural category.
  \item CTS shows the best average precision, though the quality of the retrieval is hard to determine from a given result.
  A small increase in the number of training examples has no visible influence.
  Fewer structural categories improve the retrieval accuracy.
  \item KWS has the highest recall of all techniques combined with much lower precision.
  It is the only technique where retrieval accuracy does not decrease with an increasing number of structural categories in the training examples.
\end{itemize}
We recommend PBE for use cases where the desired information is always represented in the same structural way and high confidence in the accuracy of the chunk retrieval is required.
CTS is well suited when the representation of the desired information varies slightly and the output of the chunk retrieval is further processed by a human.
In cases where the textual representation of the desired information in the log is unpredictable or varies greatly, KWS is the best technique to choose.
However, the low precision requires a human to interpret the output of the chunk retrieval.

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the contained and retrievable information in CI build logs.
  \item A model to characterize chunk retrieval techniques from CI build logs.
  %\item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several chunk retrieval techniques namely:
        \begin{itemize}
          \item program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (CTS), and
          \item a keyword search approach (KWS).
        \end{itemize}
  %\item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds manually-labelled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these substrings, and
          \item a categorization of the substrings according to their structural representation within the build log.
        \end{itemize}
  \item A study comparing the effectiveness of the three implemented techniques.
  \item Recommendations for the configuration of each of the investigated chunk retrieval techniques.
  \item Guidelines on choosing a suitable chunk retrieval technique. % TODO for a given use case or so?
\end{itemize}

This thesis first presents an overview of related research, spanning from CI, build log analysis and augmentation to system log processing.
Chapter~\ref{sec:rw} also presents existing work on information extraction and retrieval techniques and program synthesis from examples.
Next, Chapter~\ref{sec:techniques} characterizes chunk retrieval techniques and retrievable information from CI build logs.
It also introduces the three investigated techniques: PBE, CTS and KWS\@.
Chapter~\ref{sec:data-set} describes the creation of the \emph{LogChunks} data set collected from failed Travis CI build logs, including the labeling and the validation process.
Following, Chapter~\ref{sec:implementation} outlines our implementation of the three chosen chunk retrieval techniques and the usage of our unified chunk retrieval tool.
This tool is also used for the comparison described in Chapter~\ref{sec:study}.
Chapter~\ref{sec:discussion} discusses the implications of the study results and recommendations on when PBE, CTS and KWS are most suitable.
Lastly, we conclude and give an overview of further research opportunities in Chapter~\ref{sec:conclusion}.\\\\

Following you find selected graphs from the study results section. RLR stands for the baseline technique \emph{Random Line Retrieval}:

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for all techniques}
		\label{fig:success-partial-all}
\end{figure}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{one structural category}}
		\label{fig:recall-precision-singlecategory-all}
\end{figure}
\begin{figure}[htbp]
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are in \emph{multiple structural categories}}
		\label{fig:recall-precision-multicategory-all}
\end{figure}

\end{document}

### 2019-11-21 thesis/txt/3-data-set.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

\chapter{LogChunks Data Set}
\label{sec:data-set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}

originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

\section{Related Data Sets}
\todo{kind of related work for data set? the non system one moritz sent, travis torrent, check msr, new paper in rw / other rw parpers, more?}

>>>>

\chapter{LogChunks Data Set}
\label{sec:data-set}
\includegraphics[page=5, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
This chapter describes the creation of the \emph{LogChunks} data set.
\emph{LogChunks} encompasses about 800 build logs produced by a wide variety of programming languages.
For each build log we manually labeled which substring describes why the build failed.
Four our evaluation of the chunk retrieval techniques PBE, CTS and KWS we added search keywords and structural categories to each of the labeled substrings.

First, we present related data sets and show how \emph{LogChunks} differs.
Second, this chapter describes our log collection process and details the data schema of \emph{LogChunks}.
Further, it presents the labeling process and how we validated the obtained data points.
In our first validation study, a second person also labeled a sample of the build logs.
For the second validation study, we sent out mails to the original project developers to determine whether the substring we labeled actually describes the reason the build failed.

\section{Related Data Sets}
\paragraph{TravisTorrent}

### 2019-11-21 thesis/txt/5-study.tex
correct introduction a bit, introduction version to send to prof. pretschner, update plots

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-TS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsection{Common Text Similarity (CTS)}
Figure~\ref{fig:recall-precision-examplecount-TS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS\@.

Figure~\ref{fig:recall-precision-categorycount-TS} shows the same measurements for different category counts in the configuring I/O examples.
With increasing category count, precision and recall decrease.
Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.

Figure~\ref{fig:contextsizefactor-precision-recall-TS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
The recall ranges from 30\% to 55\%.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-SKWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-SKWS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factor}
		\label{fig:contextsizefactor-precision-recall-SKWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-SKWS.pdf}
		\caption{Ratio of lines retrieved with SKWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-SKWS}
	\end{minipage}
\end{figure}

\subsection{Keyword Search (KWS)}
Figure~\ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.

Figure~\ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples

Figure~\ref{fig:contextsizefactor-precision-recall-SKWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
The recall ranges from 58\% to 75\%.

Figure~\ref{fig:retrievalsizefactor-retrievalratio-SKWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
This proportion goes up to 25\% when retrieving 1.5 times more lines.

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
% 		\label{fig:precision-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
% 		\label{fig:precision-category-singularity-all}
% 	\end{minipage}
% \end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for PBE, CTS, KWS and RLR}
		\label{fig:success-partial-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared}
		\label{fig:recall-precision-all}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from a single category}
		\label{fig:recall-precision-singlecategory-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and Recall of PBE, CTS, KWS and RLR compared when configuring I/O examples are from multiple categories}
		\label{fig:recall-precision-multicategory-all}
	\end{minipage}
\end{figure}

>>>>

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-CTS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-CTS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-CTS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-CTS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsection{Common Text Similarity (CTS)}
Figure~\ref{fig:recall-precision-examplecount-CTS} presents precision and recall of chunk retrieval using CTS for different numbers of configuring I/O examples.
The count of configuring I/O examples has no visible influence on recall and precision of the chunk retrieval with CTS\@.

Figure~\ref{fig:recall-precision-categorycount-CTS} shows the same measurements for different category counts in the configuring I/O examples.
With increasing category count, precision and recall decrease.
Especially for more than three categories present we have no chunk retrieval runs where all desired lines were extracted.

Figure~\ref{fig:contextsizefactor-precision-recall-CTS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS\@.
The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
The recall ranges from 30\% to 55\%.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-KWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-KWS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-KWS.pdf}
		\caption{Precision and recall of chunk retrieval with KWS compared to retrieval size factor}
		\label{fig:contextsizefactor-precision-recall-KWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/retrievalsizefactor-retrievalratio-KWS.pdf}
		\caption{Ratio of lines retrieved with KWS compared to retrieval size factor}
		\label{fig:retrievalsizefactor-retrievalratio-KWS}
	\end{minipage}
\end{figure}

\subsection{Keyword Search (KWS)}
Figure~\ref{fig:recall-precision-examplecount-KWS} presents precision and recall of chunk retrieval using KWS in our study for different numbers of configuring I/O examples.
The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.

Figure~\ref{fig:recall-precision-categorycount-KWS} shows the same measurements for different category counts in the configuring I/O examples.
There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples

Figure~\ref{fig:contextsizefactor-precision-recall-KWS} shows the effect of the retrieval size factor on precision and accuracy of chunk retrieval runs with KWS\@.
The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
The recall ranges from 58\% to 75\%.

Figure~\ref{fig:retrievalsizefactor-retrievalratio-KWS} shows the average proportion of the lines in the test log file retrieved for different retrieval size factors with KWS\@.
When retrieving the mean number of lines in the configuring I/O examples, 15\% of the log lines are retrieved on average.
This proportion goes up to 25\% when retrieving 1.5 times more lines.

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
% 		\label{fig:precision-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
% 		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
% 		\label{fig:precision-category-singularity-all}
% 	\end{minipage}
% \end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-partial-all.pdf}
		\caption{Success of chunk retrievals for all techniques}
		\label{fig:success-partial-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-all.pdf}
		\caption{Precision and Recall of all techniques compared}
		\label{fig:recall-precision-all}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-singlecategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are from 1 category}
		\label{fig:recall-precision-singlecategory-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-multicategory-all.pdf}
		\caption{Precision and Recall of all techniques compared when training examples are >1 categories}
		\label{fig:recall-precision-multicategory-all}
	\end{minipage}
\end{figure}
